\documentclass[defaultstyle,11pt]{thesis}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%  see documentation for information about  %%%%%%%%%%
%%%%%%%%%%%  the options (11pt, defaultstyle, etc.)   %%%%%%%%%%
%%%%%%%  http://www.colorado.edu/its/docs/latex/thesis/  %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		\documentclass[typewriterstyle]{thesis}
% 		\documentclass[modernstyle]{thesis}
% 		\documentclass[modernstyle,11pt]{thesis}
%	 	\documentclass[modernstyle,12pt]{thesis}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%    load any packages which are needed    %%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{deluxetable}
\usepackage{latexsym}		% to get LASY symbols
\usepackage{graphicx}		% to insert PostScript figures
%\usepackage{deluxetable}
\usepackage{rotating}		% for sideways tables/figures
\usepackage{natbib}  % Requires natbib.sty, available from http://ads.harvard.edu/pubs/bibtex/astronat/
\usepackage{savesym}
\usepackage{amssymb}
%\savesymbol{singlespace}
\savesymbol{doublespace}
%\usepackage{wrapfig}
%\usepackage{setspace}
\usepackage{xspace}
\usepackage{color}
\usepackage{multicol}
\usepackage{mdframed}
\usepackage{url}
\usepackage{aastex_hack}
\usepackage{subfigure}
%\usepackage{emulateapj}
\usepackage{lscape}
\usepackage{grffile}
\usepackage{standalone}
\standalonefalse
\usepackage{import}
\usepackage[utf8]{inputenc}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%       all the preamble material:       %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Surveying Star Formation in the Galaxy}

\author{Adam G.}{Ginsburg}

\otherdegrees{B.S., Rice University, 2007\\
	      M.S., University of Colorado, Boulder, 2009}

\degree{Doctor of Philosophy}		%  #1 {long descr.}
	{Ph.D., Astrophysics}		%  #2 {short descr.}

\dept{Department of}			%  #1 {designation}
	{Astrophysical and Planetary Sciences}		%  #2 {name}

\advisor{Prof.}				%  #1 {title}
	{John Bally}			%  #2 {name}

\reader{Prof.~Jeremy Darling}		%  2nd person to sign thesis
\readerThree{Prof.~Jason Glenn}		%  3rd person to sign thesis
\readerFour{Prof.~Michael Shull}	%  4rd person to sign thesis
\readerFour{Prof.~Neal Evans}	%  4rd person to sign thesis

\abstract{  \OnePageChapter	% one page only ??

    I studied the formation of massive stars and clusters via millimeter,
    radio, and infrared observations.  The Bolocam Galactic Plane Survey (BGPS)
    was the first millimeter-wave blind survey of the plane of our Galaxy.  I
    wrote the data reduction pipeline for this survey and produced the final
    publicly released data products.  I ran extensive tests of the pipeline,
    using simulations to probe its performance.

    The BGPS detected over 8000 1.1 mm sources, the largest sample at this
    wavelength ever detected.  As a single-wavelength continuum survey, the
    BGPS serves as a finder chart for millimeter and radio observations.  
    I therefore performed follow-up surveys of BGPS sources in CO 3-2 and
    \formaldehyde, and others did similar follow-ups to measure velocities
    and distances towards these sources.

    \formaldehyde observations of ultracompact HII regions and other
    millimeter-bright sources were used to measure the local molecular gas
    density.  These measurements hint that density within molecular clouds does
    not follow a simple lognormal distribution.  They also show that
    star-forming clouds all contain gas at density $\gtrsim10^4$ \percc.

    I used the BGPS source catalog to identify the most massive compact clumps
    within the galaxy, identifying 18 with masses $M>10^4$ \msun in the first
    quadrant of the Galactic plane.   As these objects are all actively
    star-forming, the starless timescale of massive proto-cluster clumps must
    be relatively short, with lifetimes $\lesssim0.6$ Myr.

	}


\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	To stars and gas, for holding still for a picture.
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
	To the people who have helped, family, friends, and colleagues.

    Specific help on these projects came from Jim Braatz, Glen Langston, Phil
    Perrilat, Esteban Araya, Devin Silvia, and Jeff Mangum.  Software was
    developed in collaboration with Jordan Mirocha and Thomas Robitaille.
    Co-authors who contribute to the works in this paper include: James
    Aguirre, Jeremy Darling, John Bally, Cara Battersby, Eli Bressert, Erik
    Rosolowsky, Miranda Dunham, Manuel Merello, Timothy Ellsworth-Bowers, Jason
    Glenn, Neal Evans, ...
	}

\ToCisShort	% a 1-page Table of Contents ??

\LoFisShort	% a 1-page List of Figures ??
%	\emptyLoF	% no List of Figures at all ??

\LoTisShort	% a 1-page List of Tables ??
%	\emptyLoT	% no List of Tables at all ??


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%  footnote style; default=\arabic  (numbered 1,2,3...)
%%%%  others:  \roman, \Roman, \alph, \Alph, \fnsymbol
%	"\fnsymbol" uses asterisk, dagger, double-dagger, etc.
%	\renewcommand{\thefootnote}{\fnsymbol{footnote}}
%	\setcounter{footnote}{0}

\input macros.tex		% file containing author's macro definitions

\begin{document}
\input{introduction}

%\input{ch_iras05358}
\input{ch_w5}
\input{ch_v2}
\input{ch_boundhii}
\input{ch_h2co}
\input{ch_h2colarge}
\input{ch_software}
\input{ch_conclusion}

%\input ch2.tex			% file with Chapter 2 contents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%  Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\nocite{*}		% list all refs in database, cited or not.

%\bibliography{thesis}		% bib database file refs.bib
\bibliographystyle{apj_w_etal}	% or "siam", or "alpha", or "abbrv"
				% see other styles (.bst files) in
				% $TEXHOME/texmf/bibtex/bst

\bibliography{thesis}		% bib database file refs.bib

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%  Appendices %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix	% don't forget this line if you have appendices!

%\input appA.tex			% file with Appendix A contents
%\input appB.tex			% file with Appendix B contents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%   THE END   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

